### 2020-06-25 docs/LaTex/Paper.tex
Testing CayenneLPP encoding
Modifies docs, adds Postman environment and QuantumLeap docker files

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=76,
  caption={Pin mapping for this Dragino LoRa Shield.},
  label=ej:pin_mapping
  ]
  // Pin mapping
  const lmic_pinmap lmic_pins = {
    .nss = 10,
    .rxtx = LMIC_UNUSED_PIN,
    .rst = 9,
    .dio = {2, 6, 7},
  };
\end{lstlisting}

@@

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=64,
  caption={Variables for the potentiometer signal acquisition.},
  label=ej:potmeter_vars
  ]
  // payload to send to TTN gateway
  static uint8_t payload[3];
  static osjob_t sendjob;

  // Potentiometer pins
  int potPin = A2;               // Potmeter pin
  double potVal = 0;             // Potmeter value
\end{lstlisting}

@@

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=180,
  caption={Prpareing the payload.},
  label=ej:prep_payload
  ]
  // Prepare upstream data transmission at the next possible time.        
  // Read the analog value of the potmeter (0-1023)
  potVal = analogRead(potPin);

@@

  // adjust for the f2sflt16 range (-1 to 1)
  potVal = potVal/1023;

  // Write AGAIN the value to the serial monitor
  Serial.println(potVal);

  // float -> int
  // note: this uses the sflt16 datum (https://github.com/mcci-catena/arduino-lmic#sflt16)
  uint16_t payloadPot = LMIC_f2sflt16(potVal);

  Serial.println(payloadPot);

  // int -> bytes
  byte potLow = lowByte(payloadPot);
  byte potHigh = highByte(payloadPot);

  // place the bytes into the payload
  payload[0] = potLow;
  payload[1] = potHigh;

  // prepare upstream data transmission at the next possible time.
  // transmit on port 1 (the first parameter); you can use any value from 1 to 223 (others are reserved).
  // don't request an ack (the last parameter, if not zero, requests an ack from the network).
  // Remember, acks consume a lot of network resources; don't ask for an ack unless you really need it.
  LMIC_setTxData2(1, payload, sizeof(payload)-1, 0);
  Serial.println(F("Packet queued"));
\end{lstlisting}

So, as can be seen, in order to prepare the payload, the first is to read the analog pin and store the read value in \cmd{potVal} variable ---which is a \cmd{double} type and this makes no difference with \cmd{float} type in \enquote{On the Uno and other ATMEGA based boards} but it makes \enquote{On the Arduino Due} \cite{Ard_double_type}--- after this, the \cmd{potVal} variable is scaled to a $[0,1.0)$ range, this is due the function \cmd{LMIC\_f2sflt16()} (line 195), which is essentially a kind of encoder to encode floats to 16-bit fields. The working of this function is explained in \cite{MCCI_lmic_16bitencoder}.\footnote{A javascript decoder is also provided by the \href{https://github.com/mcci-catena/arduino-lmic\#uflt16-javascript-decoder}{\cmd{README.md}} but \doubt{it will be described in next sections.}}

@@

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=262,
  caption={Channels setup.},
  label=ej:chan_setup
  ]
  LMIC_setupChannel(0, 868100000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(1, 868300000, DR_RANGE_MAP(DR_SF12, DR_SF7B), BAND_CENTI);  // g-band
  LMIC_setupChannel(2, 868500000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(3, 867100000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(4, 867300000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(5, 867500000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(6, 867700000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(7, 867900000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(8, 868800000, DR_RANGE_MAP(DR_FSK,  DR_FSK),  BAND_MILLI);  // g2-band
\end{lstlisting}

@@

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=72,
  caption={Transmission interval.},
  label=ej:tx_interval
  ]
  // Schedule TX every this many seconds (might become longer due to duty
  // cycle limitations).
  const unsigned TX_INTERVAL = 60;
\end{lstlisting}

>>>>

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=77,
  caption={Pin mapping for this Dragino LoRa Shield.},
  label=ej:pin_mapping
  ]
  // Pin mapping
  const lmic_pinmap lmic_pins = {
    .nss = 10,
    .rxtx = LMIC_UNUSED_PIN,
    .rst = 9,
    .dio = {2, 6, 7},
  };
\end{lstlisting}

@@

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=69,
  caption={Variables for the potentiometer signal acquisition.},
  label=ej:potmeter_vars
  ]
  // Potentiometer pins
  int potPin = A2;               // Potmeter pin
  double potVal = 0;             // Potmeter value
\end{lstlisting}

@@

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=181,
  caption={Prpareing the payload.},
  label=ej:prep_payload
  ]
  // Prepare upstream data transmission at the next possible time.

  // Read the analog value of the potmeter (0-1023)
  potVal = analogRead(potPin);

@@

  // prepare upstream data transmission at the next possible time.
  // transmit on port 1 (the first parameter); you can use any value from 1 to 223 (others are reserved).
  // don't request an ack (the last parameter, if not zero, requests an ack from the network).
  // Remember, acks consume a lot of network resources; don't ask for an ack unless you really need it.

  lpp.reset();
  lpp.addAnalogInput(1, potVal);

  LMIC_setTxData2(1, lpp.getBuffer(), lpp.getSize(), 0);
  Serial.println(F("Packet queued"));
\end{lstlisting}

So, as can be seen, in order to prepare the payload firstly the analog pin is stored in \cmd{potVal} variable, after this the function \cmd{lpp.reset()} is ued to reset the CayenneLPP buffer, then the measure \cmd{potVal} is added to the CayenneLPP buffer in the first channel using the function \cmd{lpp.addAnalogInput()}, finally the  \doubt{REDO}
%So, as can be seen, in order to prepare the payload, the first is to read the analog pin and store the read value in \cmd{potVal} variable ---which is a \cmd{double} type and this makes no difference with \cmd{float} type in \enquote{On the Uno and other ATMEGA based boards} but it makes \enquote{On the Arduino Due} \cite{Ard_double_type}--- after this, the \cmd{potVal} variable is scaled to a $[0,1.0)$ range, this is due the function \cmd{LMIC\_f2sflt16()} (line 195), which is essentially a kind of encoder to encode floats to 16-bit fields. The working of this function is explained in \cite{MCCI_lmic_16bitencoder}.\footnote{A javascript decoder is also provided by the \href{https://github.com/mcci-catena/arduino-lmic\#uflt16-javascript-decoder}{\cmd{README.md}} but \doubt{it will be described in next sections.}}

@@

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=248,
  caption={Channels setup.},
  label=ej:chan_setup
  ]
  LMIC_setupChannel(0, 868100000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(1, 868300000, DR_RANGE_MAP(DR_SF12, DR_SF7B), BAND_CENTI);  // g-band
  LMIC_setupChannel(2, 868500000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(3, 867100000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(4, 867300000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(5, 867500000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(6, 867700000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(7, 867900000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(8, 868800000, DR_RANGE_MAP(DR_FSK,  DR_FSK),  BAND_MILLI);  // g2-band
\end{lstlisting}

@@

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=73,
  caption={Transmission interval.},
  label=ej:tx_interval
  ]
  // Schedule TX every this many seconds (might become longer due to duty
  // cycle limitations).
  const unsigned TX_INTERVAL = 60;
\end{lstlisting}
